### 2013-06-08 MSWL_ECO_lesson4.tex
Revision chapter 4

FLOSS

The one million dollar question \emph{Which model has success.}

@@

If the company

Si la empresa no utilizara FLOSS no sería una empresa viable, es decir, sin el
 uso de FLOSS la empresa no existiría.

@@

Otra tendencia, es la estrategia de liberar distintas distribuciones de 
software como FLOSS para crear una comunidad libre alrededor.

@@

>>>>

The one million dollar question \emph{Which model has success?.}

@@

If the company did not use FLOSS would not be a viable, that is,  without the
  FLOSS use the company would not exist.

@@

Another trend is the strategy of releasing different distributions of
FLOSS software to create a free community around.

@@

The business model must always pivot on the use value, not on the sale value.
\\

There are 3 axes influencing  software landscape: Software model, development model, and  business model.

Nowadays, use of libre software would reach more than 90 \% of companies worldwide. We could say that almost every company has a strategy about libre software.

The  Carlo Daffara taxonomy (FLOSSMETRICS) of business model and examples
\begin{itemize}
    \item         Dual licensing, e.g. MySQL, Mozilla software, Sleepycatdb, Pentaho
    \item         Open Core, e.g. Zimbra, SugarCRM, Eucalyptus, SendMail
     \item        Product specialists, e.g. Alfresco
    \item        Platform Providers, e.g. RedHat, OpenStack
     \item        Selection/consulting companies, e.g. Navica, Open WebApps
     \item        Aggregate support providers, e.g. OpenLogic
     \item        Legal certification and insurance, e.g. Palamida
    \item         Training and documentation, e.g. Gbdirect
     \item        R\&D cost sharing, e.g. Eclipse, Webkit, OpenStack, Maemo (Nokia)
     \item        Indirect revenues, e.g. Firefox, Android, Perl (O'Reilly)
\end{itemize}
